Safe and Robust Formal Synthesis of Digital Controllers for Continuous Plants

### 2018-03-15 automatica/paper.tex
changes \sigma to \phi for consistency

The input specification provided to CEGIS is of the form
$\exists P .\, \forall a.\, \sigma(a, P)$, where $P$ ranges over functions
(where a function is represented by the program computing it),
$a$ ranges over ground terms, and $\sigma$ is a quantifier-free formula. 
We~interpret the ground terms over some finite domain~$\mathcal{D}$.
%

The design of our synthesizer consists of two phases, an inductive
synthesis phase (denoted by {\sc Synthesize} in
Figure~\ref{fig:CEGIS}) and a validation phase (denoted by {\sc
  Verify}), which interact via a finite set of test vectors {\sc
  inputs} that is updated incrementally.  Given the aforementioned
specification $\sigma$, the inductive synthesis procedure tries to
find an existential witness $P$ satisfying the specification
$\sigma(a, P)$ for all $a$ in {\sc inputs} (as opposed to all $a \in
\mathcal{D}$).
%
If the synthesis phase succeeds in finding a witness~$P$, this witness is a
candidate solution to the full synthesis formula.  We pass this candidate
solution to the validation phase, which checks whether it is a full solution
(i.e., $P$ satisfies the specification $\sigma(a, P)$ for all
$a\in\mathcal{D}$).  If this is the case, then the algorithm terminates. 
Otherwise, additional information is provided to the inductive synthesis
phase in the form of a new counterexample that is added to the {\sc inputs}
set and the loop iterates again.  %% More details about the general
%% architecture of the synthesizer can be found
%% in~\cite{DBLP:conf/lpar/DavidKL15}.

@@

While in the previous section we discussed the generic CEGIS
framework, in the rest of the paper we will explain how we adapt it to
the synthesis of digital controllers. For this purpose, we start by
describing the specific property that we pass to the synthesizer as
the specification $\sigma$. Namely, we are interested in capturing
stability and safety, which we discuss in Sections~\ref{ssec:stabspecification}
and~\ref{ssec:safespecification}, respectively.

>>>>

The input specification provided to CEGIS is of the form
$\exists P .\, \forall a.\, \phi(a, P)$, where $P$ ranges over functions
(where a function is represented by the program computing it),
$a$ ranges over ground terms, and $\phi$ is a quantifier-free formula. 
We~interpret the ground terms over some finite domain~$\mathcal{D}$.
%

The design of our synthesizer consists of two phases, an inductive
synthesis phase (denoted by {\sc Synthesize} in
Figure~\ref{fig:CEGIS}) and a validation phase (denoted by {\sc
  Verify}), which interact via a finite set of test vectors {\sc
  inputs} that is updated incrementally.  Given the aforementioned
specification $\phi$, the inductive synthesis procedure tries to
find an existential witness $P$ satisfying the specification
$\phi(a, P)$ for all $a$ in {\sc inputs} (as opposed to all $a \in
\mathcal{D}$).
%
If the synthesis phase succeeds in finding a witness~$P$, this witness is a
candidate solution to the full synthesis formula.  We pass this candidate
solution to the validation phase, which checks whether it is a full solution
(i.e., $P$ satisfies the specification $\phi(a, P)$ for all
$a\in\mathcal{D}$).  If this is the case, then the algorithm terminates. 
Otherwise, additional information is provided to the inductive synthesis
phase in the form of a new counterexample that is added to the {\sc inputs}
set and the loop iterates again.  %% More details about the general
%% architecture of the synthesizer can be found
%% in~\cite{DBLP:conf/lpar/DavidKL15}.

@@

While in the previous section we discussed the generic CEGIS
framework, in the rest of the paper we will explain how we adapt it to
the synthesis of digital controllers. For this purpose, we start by
describing the specific property that we pass to the synthesizer as
the specification $\phi$. Namely, we are interested in capturing
stability and safety, which we discuss in Sections~\ref{ssec:stabspecification}
and~\ref{ssec:safespecification}, respectively.
